Improving the communication and transparency of stock assessment using interactive

### 2018-10-25 manuscript.Rmd
Drafting paragraph on interactive visualization tools

@@

"We are in an age of data-intensive science and big data, and ecologists must develop the capabilities to deal with their data." [@hampton2013]

>>>>

In the age of data-intensive science and big data, scientists across many fields are faced with the challenge of synthesizing and communicating information from large and complex data sets. Scientific data are often presented as tabular summaries and static plots, however, seeing patterns in tables can be difficult and static plots are divorced from the underlying data. This limits our ability to explore the underlying data in more detail by, for instance, zooming into areas of interest. New open source tools are bridging this gap by making it easier to build interactive figures [@perkel2018]. In particular, browser-based data visualizations have been playing an increasing prominent role in communicating information on a wide range of topics. Interactive graphics are frequently utilized by media outlets, such as the New York Times, and scientists from a wide range of disciplines are starting to apply interactive visualization tools to explore and communicate their results [@yeatman2018; @tushar2017; @wick2015].

JavaScript libraries, such as D^3^ [@bostock2011], for visualizing data on modern web-browsers now match or exceed the abilities of most platform-specific software and the development of high-level libraries ... plotly ... python ... R

@@

In this data-intensive era of stock assessment, one of the difficulties becomes visualizing the inputs and outputs to integrated stock assessment models. The standard approach has been to create a series of tables and static plots to help assess the inputs and model fits. Data presented in tables is incredibly valuable, but as human beings, seeing patterns can be challenging. Static figures, in contrast, help reveal patterns but they are divorced from the underlying data and, as such, limit detailed explorations. New tools are bridging this gap by making it easier to build interactive figures [@perkel2018].

Interactive visuals...visual representation of the data and model that help us interpret complex data at a glance https://campus.sagepub.com/blog/3-benefits-of-interactive-visualization

https://centricdigital.com/blog/digital-trends/the-value-of-interactive-data-visualization-and-why-it-matters-to-business/

Good example from Keith: https://www.nature.com/articles/s41467-018-03297-7

https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/120103

https://www.nature.com/articles/d41586-018-01322-9
